\documentclass[a4paper,12pt]{article}


%\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{pxfonts}

%\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{ifpdf}
\usepackage{pdfpages}
\pagestyle{fancy}

\ifpdf
        \DeclareGraphicsRule{*}{mps}{*}{}
\fi

%utf 8 + cjk support
%cjkbg5,cjkgb,cjkjis
%\usepackage[cjkjis]{ucs}
%\usepackage[cjkjis]{ucs}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{CJK}
%\usepackage[uni-87]{inputenc}


\title{\vspace{-1cm}Committee Meeting $X$\\Meeting Minutes}
\author{Physics Students' Society\\Unconfirmed Minutes}
\date{XX.XX XM AEXT, Xxxday XX${}^{\mathrm{xt}}$ Xxxxber XXXX\\Final Revision {\tiny\it rev 1}}

\headheight 15pt

\rhead[\thepage]{Committee Meeting $X$}
\lhead[\thepage]{Physics Students' Society}
\chead[\thepage]{}

\newlength{\lheight}
\settoheight{\lheight}{X}

\renewcommand{\labelenumi}{\thesection.\arabic{enumi}.}
\newcommand{\itemi}[1]{\addcontentsline{toc}{subsection}{#1} \bf #1}

\newcommand{\motion}[5]{
\par \hspace{#5} \fbox{
\begin{minipage}{1\columnwidth}
		{\sc Motion:} #1 \vspace{5mm} \\ \hspace{-30mm}
%		\begin{tabular*}{\columnwidth}{llr}
		\begin{tabular}{p{0.35\textwidth}p{0.49\textwidth}r}
		\hspace{-2.5mm}{\sc Mover:} #2 & {\sc Seconder:} #3 & {\bf #4}
		\end{tabular}
\end{minipage}}}

\newcommand{\divisionmotion}[6]{
\par \hspace{#5} \fbox{
\begin{minipage}{1\columnwidth}
		{\sc Motion:} #1 \vspace{5mm} \\ \hspace{-30mm}
%		\begin{tabular*}{\columnwidth}{llr}
		\begin{tabular}{p{0.35\textwidth}p{0.49\textwidth}r}
		\hspace{-2.5mm}{\sc Mover:} #2 & {\sc Seconder:} #3 & {\bf #4}
		\end{tabular}
		#6%\vspace{-\lheight}
\end{minipage}}}

\begin{document}
\maketitle
\begin{description}
\item[Name of Club] Physics Students' Society
\item[Type of Meeting] Committee Meeting
\item[Meeting Ordinal Number] XXXX/XX
\item[Date and Time of Meeting] XX.XX AEXT XXXday XX${}^{\mathrm{xt}}$ Xxxxber
\item[Venue of Meeting] Meeting Venue
\end{description}
\tableofcontents
\section{Attendance}
\begin{enumerate}
\item Meeting opened at XX.XX AEXT.\\
Chairperson---President of the Society, Daniel Rodgers-Pryor\\
Minute taker---Secretary of the Society, Patrick Clearwater
\motion{That Daniel RP be the chairperson and that Patrick Clearwater take minutes.}{Emma Bland}{Patrick Clearwater}{CWD}{-\leftmargin}
\item Reaching quorum\footnote{{\it Constitution of the Physics Students' Society}, 11(b)}, the following people were present:
	\begin{itemize}
	\item Emma Bland {\small President}
	\item Patrick Clearwater {\small Secretary}
	\item Daniel Flynn {\small General Committee}
	\item Matt Greer {\small General Committee}
	\end{itemize}
\item Apologies\\
	No apologies where recieved.
\end{enumerate}
\section{Adoption of the Agenda}
\motion{That the agenda be adopted.}{Patrick Clearwater}{Emma Bland}{CWD}{0 cm}
\section{Confirmation of Minutes}
\addcontentsline{toc}{subsection}{Minutes of meeting 2009/03.}
\motion{That the minutes of the meeting 2009/03 are a true and accurate record
of the business of that meeting.}{}{Angus McInnes}{CWD}{0 pt}
\section{General Business}
\begin{enumerate}
\item {\itemi{ item }}
\motion{ the }{proposer}{seconder}{CWD}{-\leftmargin}
\item {\itemi{Other business}}
No other business was tabled.
\end{enumerate}
\section{Meeting closed}
The chairperson closed the meeting at XX.XX AM.

\vspace{1cm}
\rule{\columnwidth}{\fboxrule}
\par
\vspace{1cm}
\par\noindent
Published by the authority of the Secretary of the Society.
\end{document}
